\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Get Pocket blurb,
%	https://getpocket.com/explore/item/how-to-make-banana-bread?utm_source=pocket-newtab
]
{Quick Banana Bread}

    \ingredients
    {
		8 & Tbsp butter, melted\\
		198 & g granulated sugar \\
		 & \\
		2 & eggs \\
		 & \\
		$\sfrac{1}{4}$ & cup milk \\
		1 & tsp vanilla extract \\
		 & \\
		3 & bananas, very ripe \\
		 & \\
		240 & g AP flour \\
		1 & tsp baking soda \\
		$\sfrac{1}{4}$ & tsp salt \\
    }
    
    \preparation
    {
        \step Preheat the oven to 350$^{\circ}$F and arrange a rack in the bottom third of the oven. 
		\step Line a~8"x 5" loaf pan with parchment paper, letting the excess hang over the long sides to form a sling. Spray the inside with cooking spray. 
		\step Combine the melted butter and sugar in a mixing bowl and stir until combined. 
		\step Add the eggs and mix until completely combined and smooth. 
		\step Mix in the milk and vanilla extract. \\
		\step Mash the bananas in a separate bowl and stir the bananas into the batter. 
		\step In a separate bowl, combine flour, baking soda, and salt. Gradually add into the batter; stop mixing just before the dry ingredients are fully incorporated.
		\step Using a spatula, finish incorporating the dry ingredients and pour into the prepared pan. Smooth the top of the batter. 
		\step Bake for 50~to 65~minutes, until a toothpick or cake tester inserted comes out clean. Baking time will vary slightly depending on the moisture and sugar content of your bananas -- start checking around 50~minutes and then every 5~minutes after. 
		\step Cool in the pan for 10~minutes, then remove the loaf from the pan using the parchment sling and place on the cooling rack. 
    }
	
	\suggestion
	{
		To freeze: Wrap in plastic wrap and then aluminum foil and freeze for up to three months. 
	}

\end{recipe}
