\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Bison burger at 80/20 in Norfolk,
	%https://www.allrecipes.com/recipe/238315/grilled-bison-burgers/
]
{Bison Burger}

    \ingredients
    {
		1 & lb ground bison \\
		$\sfrac{1}{2}$ & cup Panko bread crumbs \\
		1 & egg \\
		3 & Tbsp Worcestershire Sauce \\
		dash & garlic powder and black pepper \\
		4 & slices of gruyere \\
		 & \\
		& cooked bacon \\
		 & \\
		2-3 & yellow onions, caramelized \\		
    }
    
    \preparation
    {
        \step Mix bison, crumbs, egg, Worcestershire sauce, and seasonings together by hand in a bowl; form into 4~patties. 
		\step Add drizzle of oil to large skillet and heat to medium or medium-high heat. When you see a wisp of smoke, add patties. Cook for 3 to 5 minutes, then flip patties. Add gruyere, cover pan with lid, and cook another 3 to 5 minutes. 
		\\
		\\
		\\
		\\
		\\
    }
    
	\suggestion[Caramelized Onion]
	{
		Slice onions. Heat olive oil (and/or butter) over medium heat, add onions. After 10 minutes, add dash of sugar and lower heat. Cook, stirring every few minutes. Towards the end, add splash of balsamic vinegar. Takes $\sim$1 hour, less if the ratio of space to onion is high. \\(5~onions $\approx$ 2 cups)
	}
	
    \suggestion[Suggested cooking times:]
    {
	   \begin{itemize}
	   \item[] Medium-Rare (red): 6 minutes total, 130-135$^{\circ}$F
	   \item[] Medium (pink): 7 to 8 minutes total, 140-145$^{\circ}$F
	   \item[] Medium Well (hint of pink): 9 minutes total, 150-155$^{\circ}$F
	   \item[] Well  Done (no pink): 10 minute total, 160$^{\circ}$F
	   \end{itemize}
    }
	
	\hint
	{
		Stonewall Kitchen Roasted Garlic Aioli
	}

\end{recipe}
