\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Originally Starbucks,
%	https://www.lilcookie.com/starbucks-copycat-blueberry-muffins/
]
{Starbucks Copycat Blueberry Muffins}

    \ingredients
    {
		\multicolumn{2}{l}{\textbf{For the muffins}} \\
		7 & Tbsp butter, soft \\
		200 & g granulated sugar \\
		$\sfrac{1}{2}$ & tsp salt \\
		1 & tsp vanilla extract \\
		 & \\
		2 & eggs \\
		 & \\
		280 & g AP flour \\
		2 & tsp baking powder \\
		 & \\
		$\sfrac{1}{2}$ & cup milk \\
		 & \\
		200 & g blueberries, frozen or fresh \\
		\multicolumn{2}{l}{\textbf{For the streusel topping}} \\
		40 & g light brown sugar \\
		50 & g AP flour \\
		2 & Tbsp cold butter cut into cubes \\
		dash & salt \\
    }
    
    \preparation
    {
        \step Preheat the oven to 350$^{\circ}$F and arrange paper cups in a muffin pan. 
		\step In a mixer bowl with paddle attachment, mix butter, sugar, salt, and vanilla until you get a soft and creamy mixture. 
		\step Add eggs one by one, beating continuously until incorporated. 
		\step Mix flour and baking powder in a small bowl. \\
		\step Add roughly $\sfrac{1}{3}$ of the flour into mixture while blending slowly. 
		\step Add $\sfrac{1}{2}$ of the milk while blending until it is mixed into the batter. 
		\step Add another $\sfrac{1}{3}$ of the flour while mixing, then the remaining milk, and finally the remaining flour. Once the mixture is smooth, stop mixing; over-mixing may damage the texture of the muffins. 
		\step Add in the frozen blueberries and mix briefly by hand only until evenly dispersed in the mixture. 
		\step Fill the muffin cups in with batter. \\
		\step \textbf{To make the streusel topping:} Place sugar, flour, butter, and salt in a bowl and blend with fingertips until you get a crumbly mixture. Sprinke generously on top of each muffin. 
		\step Bake for 20 to 25 minutes or until the muffins are golden and set. (Kirsten's suspect muffin pan requires 35 to 40 minutes.)
    }
	
	\suggestion
	{
		Keep the muffins in a closed container in the refrigerator for up to 6 days; it is recommended to serve the muffins warm or at room temperature.
	}

\end{recipe}
