\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Aunt Rita,
]
{Bread and Butter Pickles}
    
    \ingredients
    {
		8 & lb salad cucumbers \\
		4 & lb white onions \\
		2 & green bell peppers \\
		$\sfrac{1}{2}$ & cup canning salt \\
		 & \\
		5 & cups cider vinegar \\
		5 & cups sugar \\
		2 & Tbsp mustard seed \\
		$\sfrac{1}{2}$ & tsp celery seed \\
		$\sfrac{1}{2}$ & tsp whole cloves \\
		1 & tsp turmeric \\
    }
    
    \preparation
    {
        \step Wash all vegetables and slice as thin as possible (strongly suggest using food processor). Layer half the cucumbers, onions, peppers, and salt (in that order) -- repeat with remaining ingredients. 
		\step Let stand for at least 3~hours (overnight is fine), covered with a towel; occasionally, stir so that bottom ingredients move up and vice versa. Drain. 
		\step Combine vinegar, sugar, and spices in large pan; bring to boil. 
		\step Add drained vegetables; heat thoroughly but do not boil. Occasionally, stir so that bottom ingredients move up and vice versa; do not cook the veggies. 
		\step Pack while hot into sterilized jars and seal at once. Should make about 9~jars. 
    }

	\suggestion[Choosing Cucumbers]
	{
		Cucumbers should be around 6-inches long and 1.5-inches diameter. 
	}
	
	\suggestion[Sterilizing Jars]
	{
		Fill a large pot with water, jars, lids, and bands -- make sure all surfaces are covered. Bring to a boil, then let boil for 10~minutes. Remove from water with tongs, fill using canning funnel, wipe top, and cover with lid and band -- screw band tightly. If it successfully seals, you will hear a popping sound -- once cooled, you should not be able to depress the lid. If it doesn't seal, pickles must be stored in the fridge; if a previously sealed jar becomes unsealed in the pantry, toss it. 
	}

\end{recipe}
