\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Indian take out,
	%https://cafedelites.com/butter-chicken/
]
{Butter Chicken}

    \ingredients
    {
		\multicolumn{2}{l}{\textbf{For the chicken marinade}} \\
		1$\sfrac{3}{4}$ & lb boneless, skinless chicken thighs or breasts, cut into bite-sized pieces \\
		$\sfrac{1}{2}$ & c plain yogurt \\
		1$\sfrac{1}{2}$ & Tbsp minced garlic \\
		1 & Tbsp ginger, minced or finely grated \\
		2 & tsp garam masala \\
		1 & tsp tumericc \\
		1 & tsp ground cumin \\
		1 & tsp red chili powder \\
		1 & tsp salt \\
		\multicolumn{2}{l}{\textbf{For the sauce}} \\
		2 & Tbsp ghee (1 Tbsp butter + 1 Tbsp oil) \\
		1 & large onion, sliced or chopped \\
		1$\sfrac{1}{2}$ & Tbsp garlic, minced \\
		1 & Tbsp ginger, minced or finely grated \\
		1$\sfrac{1}{2}$ & tsp ground cumin \\
		1$\sfrac{1}{2}$ & tsp garam masala \\
		1 & tsp ground coriander \\
		14 & oz crushed tomatoes \\
		1 & tsp red chili powder (adjustable) \\
		1$\sfrac{1}{4}$ & tsp salt \\
		1 & c heavy cream \\
		1 & Tbsp sugar \\
		$\sfrac{1}{2}$ & tsp kasoori methi (or dried fenugreek leaves) \\
    }
    
    \preparation
    {
        \step In a bowl, combine chicken with all of the ingredients for the chicken marinade; let marinate for 30 to 60 minutes (or overnight, if time allows).
		\step Heat oil in a large skillet or pot over medium-high heat. When sizzling, add chicken pieces in two or three batches, making sure not to crowd the pan. Fry each batch until browned, about 3 minutes. Set aside and keep warm. 
		\step Heat ghee in the same pan. Fry the onions until they start to sweat, about 6 minutes, while scraping up any browned bits stuck on the bottom of the pan. 
		\step Add garlic and ginger and saut\'e for 1 minute until fragrant, then add ground coriander, cumin, and garam masala. Let cook for about 20 seconds until fragrant, while stirring occasionally. 
		\step Add crushed tomatoes, chili powder, and salt. Let simmer for about 10 to 15 minutes, stirring occasionally until sauce thickens and becomes a deep brown red colour. 
		\step Remove from heat, scoop mixture into a blender and blend until smooth. You may need to add a couple tablespoons of water to help it blend (up to $\sfrac{1}{4}$ cup). Work in batches depending on the size of your blender.
		\step Pour the pur\'eed sauce back into the pan. Stir in the cream, sugar, and crushed kasoori methi / fenugreek leaves through the sauce. 
		\step Add the chicken with juices back into the pan and cook for an additional 8 to 10 minutes until chicken is cooked through and the sauce is thick and bubbling. 
		%\step Garnish with chopped cilantro and serve with fresh, hot garlic butter rice or fresh homemade Naan bread. 
    }
	
	\suggestion[Optional]
	{
		To thin out the sauce, add a couple tablespoons of ghee or butter at the end of cooking, and gently simmer it through. Alternatively, add a small amount of water. Freezer safe!
	}


\end{recipe}
