\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = blog via Jess via Elise,
	%http://forme-foryou.com/2011/08/the-only-chocolate-chip-cookie-i-will-ever-need-to-know-how-to-make-for-the-rest-of-my-life.html
]
{Chocolate Chip Cookies}

    \ingredients
    {
		8$\sfrac{1}{2}$ & oz cake flour \\
		 & (2 cups - 2 Tbsp) \\
		8$\sfrac{1}{2}$ & oz bread flour \\
		 & (1$\sfrac{2}{3}$ cups) \\
		1$\sfrac{1}{4}$ & tsp baking soda \\
		1$\sfrac{1}{2}$ & tsp baking powder \\
		1$\sfrac{1}{2}$ & tsp coarse salt, such as kosher \\
		 & \\
		1$\sfrac{1}{4}$ & cups unsalted butter \\
		 & (2$\sfrac{1}{2}$ sticks, 10 oz) \\
		10 & oz light brown sugar \\
		 & (1$\sfrac{1}{4}$ cups) \\
		8 & oz granulated sugar \\
		 & (1 cup + 2 Tbsp) \\
		 & \\
		2 & eggs \\
		2 & tsp vanilla extract \\
		 & \\
		20 & oz chocolate chips, 60\% cacao (Ghiradelli) \\
		 & \\
		dash & sea or kosher salt \\
    }
    
    \preparation
    {
        \step Combine flours, baking soda, baking powder, and salt in a bowl. Whisk well; then set aside. 
		\step Using a mixer fitter with a paddle attachment, cream butter and sugars until very light and fluffy. 
		\step Add the eggs, one at a time, mixing well after each addition. Mix in the vanilla. Scrape down the sides of the bowl with a rubber spatula as need.
		\step Reduce the mixer speed to low; then add dry ingredients, and mix until just combined. 
		\step Add the chocolate chips, and mix briefly to incorporate.
		\step Press plastic wrap against the dough, and refrigerate for 24 to 36 hours. The dough may be used in batches, and can be refrigerated for up to 72 hours.
		\step Preheat oven to 350$^{\circ}$F. Remove dough from the refrigerator  and allow it to soften slightly. Line a baking sheet with parchment paper or a nonstick baking mat.
		\step Scoop six mounds of cookie dough -- about $\sfrac{1}{3}$ of a cup (\#12 scoop) -- onto the baking sheet, making sure to space them evenly. Sprinkle lightly with sea salt, and bake until golden brown but still soft, 15 to 20 minutes. 
		\step Transfer the baking sheet to a wire rack for 10 minutes, then transfer the cookies onto the rack to cool a bit more. 
    }
	
	\suggestion
	{
		All ingredients should be room temperature. \\ \\
		Pre-shaped cookie mounds can be frozen for later use and baked directly out of the freezer (leave cookies on sheet during oven heating). \\ \\
		18 - 24 cookies
	}


\end{recipe}
