\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = King Arthur Baking,
%	https://www.kingarthurbaking.com/recipes/cinnamon-raisin-sourdough-bread-recipe
]
{Cinnamon Raisin Sourdough Bread}

    \ingredients
    {
		\multicolumn{2}{l}{\textbf{Dough}} \\
		113 & g sourdough starter, ripe or discard \\
		361 & g unbleached AP flour \\
		2\sfrac{1}{2} & tsp instant yeast \\
		1 & Tbsp sugar \\
		1\sfrac{1}{4} & tsp salt \\
		1 & large egg \\
		5 & Tbsp unsalted butter, softened \\
		152 & g lukewarm water \\
		\multicolumn{2}{l}{\textbf{Filling}} \\
		50 & g sugar \\
		1\sfrac{1}{2} & tsp cinnamon \\
		2 & tsp AP flour \\
		1 & large egg beaten with 1~Tbsp water \\
		74 & g raisins \\
    }
    
    \preparation
    {
        \step \textbf{To make the dough:} Combine all of the dough ingredients, mix, and knead -- using your hands, a stand mixer, or a bread machine set on the dough cycle -- to make a soft, smooth dough. 
		\step Place the dough in a lightly greased container, and allow it to rise for 1\sfrac{1}{2} to 2~hours, until it's just about doubled in bulk. 
		\step While the dough is rising, make the filling by stirring together the sugar, cinnamon, and flour. 
		\step Gently deflate the dough, and transfer it to a lightly greased work surface. 
		\step Roll (floured rolling pin) and pat the dough into a rough rectangle approximately 6"x 20". 
		\step Brush the dough with the egg/water mixture and sprinkle it evenly with the filling and raisins, leaving a bare strip about 1" wide along one short edge; this will make it easier to seal. 
		\step Starting with the short end that's covered with filling, roll the dough into a log. Pinch the ends to seal, and pinch the long seam closed. 
		\step Transfer the log, seam-side down, to a lightly greased 9"x 5" loaf pan. Cover and allow the bread to rise until it's crested about 1" over the rim of the pan, about 1 hour. 
		\step While the dough is rising, preheat the oven to 350$^{\circ}$F. \\
		\step Bake the bread uncovered for 15 minutes. Place aluminum foil tent lightly over pan and cook for a further 25 to 30 minutes. The bread's crust will be light golden brown, and the interior of the finished loaf should be 190$^{\circ}$F. 
		\step Remove the bread from the oven, and gently loosen the edges. Turn it out of the pan, and brush the surfaces with a knob of butter; this will give it a soft, satiny crust. Allow the bread to cool completely before slicing. 
    }

\end{recipe}
