\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Mom,
%	https://cafedelites.com/15-minute-creamy-tomato-garlic-butter-shrimp/
]
{Creamy Tomato Garlic Butter Shrimp}

    \ingredients
    {
		2 & Tbsp olive oil \\
		2 & yellow onions, diced \\
		6 & garlic cloves, minced \\
		1 & lb raw shrimp, peeled and deveined \\
		2 & tsp dried basil \\
		$\sfrac{1}{2}$ & tsp salt \\
		 & \\
		24 & oz jar of passata or marinara sauce \\
		1 & chicken bullion cube, crushed \\
		2 & tsp parsley \\
		1 & tsp black pepper \\
		dash & sugar \\
		$\sfrac{1}{2}$ & tsp salt \\
		 & \\
		1$\sfrac{1}{3}$ & cup milk (or half and half or heavy cream) \\
		 & \\
		 & parmesan to garnish \\
    }
    
    \preparation
    {
        \step Heat the olive oil in a large skillet or pan over medium heat. Add the onion and saute until transparent. 
		\step Stir in the garlic and fry until fragrant ($\sim$30~seconds), then add in the shrimp with the basil and $\sfrac{1}{2}$~teaspoon salt.
		\step Saute shrimp for 2~minutes on one side; flip and continue to saute on the other side for a further minute. 
		\step Quickly add in the sauce, crushed bullion cube, parsley, pepper, sugar, and remaining salt. 
		\step Allow the sauce to heat through for another minute before adding the milk (or cream). Continue cooking for a further minute or until the shrimp are cooked through. 
		\step Toss cooked pasta with creamy tomato sauce until combined. 
    }

	\hint
	{
		Cooked shrimp have an exterior that's pink and a little ``white'' in color and is curled in a `C'-shape. If it's bright white, or curled on itself, they're probably overcooked. 120$^{\circ}$
	}

\end{recipe}
