\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Zingerman's via Jim,
]
{Farm Bread}

    \ingredients
    {
		580 & g water, room temp \\
		145 & g Zingerman's Levain \\
		72 & g whole wheat flour \\
		865 & g AP flour \\
		23 & g sea salt \\
    }
    
    \preparation
    {
        \step Place the water in the mixing bowl. Tear the levain into small pieces and add to the water. Add the whole wheat flour and half of the AP flour (432.5~g). Stir with a wooden spoon to combine and break up the levain. Add the remaining AP flour and salt. Mix to combine until the dough is rough and shaggy. 
		\step Turn the dough out onto a clean, unfloured work surface, scraping any bits of flour or dough out of the bowl. Knead the dough for 6 to 8 minutes. 
		\step Lightly oil a container and place the dough into the container. Cover with plastic. Let the dough ferment for 1 hour. 
		\step Place the dough on a lightly floured work surface and fold for the first time. Place it back into the container and cover with plastic. Ferment for 1 hour. 
		\step Place the dough on a lightly floured work surface and fold for the second time. Place it back into the container and cover. Ferment for 1 hour. 
		\step Place the dough on a lightly floured work surface and fold for the third time. Place it back into the container and cover. Ferment for 1 hour. 
		\step Lightly flour the work surface and place the dough on the surface. Divide the dough into two equal portions. Pre-shape each into a round, cover, and let relax for 45 minutes. 
		\step Prepare two proofing baskets (9-inch rounds) by lightly flouring each basket. \\
		\step Shape each round into a boule and place into the baskets with the seam side up. Let ferment for $3\sfrac{1}{2}$ hours at room temperature. Use the touch test to see if the loaves are ready for the oven. 
		\step Preheat the oven with a baking stone and cast iron skillet to 450$^{\circ}$~F roughly 45 minutes before baking. 
		\step Turn the loaves out of the basket onto parchment paper placed on top of a baking peel and score. Place second loaf in fridge if your baking stone won't fit both loaves simultaneously. 
		\step Slide the loaf (or loaves) onto the preheated baking stone and bake for 8 minutes with steam, covered. Uncover and bake for an additional 35 to 40 minutes, until the crust is a dark brown. Remove from oven and cool on cooling rack. Cool completely before cutting. 
    }
	
	\suggestion[Folding]
	{
		Shape the dough into a rectangle. Fold $\sfrac{1}{3}$ of the dough toward the center and then fold $\sfrac{1}{3}$ of the dough from the other side over that. Repeat vertically, and place the ``package'' of dough seam side down into the proofing container. 
	}
	
	\suggestion[Touch test]
	{
		Poke the bread with a finger. The loaf is ready when the indentation pushes back very slowly and doesn't completely fill back in. If it immediately pushes back out, check again in 15 minutes; if it doesn't spring back at all, bake immediately and score very lightly. 
	}
	
	\suggestion[Baking with steam]
	{
		Place ice cubes into preheated cast iron skillet, place loaves onto baking stone, and cover loaves - making sure cover extends over edge of baking stone, allowing it to capture steam produce by ice cubes. 
	}

\end{recipe}
