\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {An age},
%    portion = \portion{5},
    source = Carb craving with Indian,
%	https://cafedelites.com/buttery-garlic-naan-recipe/
]
{Garlic Naan}
    
    \ingredients
    {
		\multicolumn{2}{l}{\textbf{Naan breads}} \\
		$\sfrac{1}{4}$ & c warm water \\
		2 & tsp sugar \\
		1$\sfrac{1}{2}$ & tsp active or instant dry yeast \\
		$\sfrac{3}{4}$ & c warm milk \\
		$\sfrac{3}{4}$ & c plain Greek yogurt (full fat) \\
		$\sfrac{1}{4}$ & c vegetable oil \\
		2 & cloves garlic, minced \\
		480 & g AP flour \\
		1 & tsp baking powder \\
		1 & tsp salt \\
		\multicolumn{2}{l}{\textbf{Garlic butter topping}} \\
		3 & Tbsp butter, melted \\
		2 & cloves garlic, minced \\
		1 & tsp fresh cilantro or parsley \\
    }
    
    \preparation
    {
        \step \textbf{To make the bread:} Combine the water, sugar, and yeast together. Let sit for 5 to 10 minutes or until the mixture begins to bubble on top. 
		\step Add in the milk, yogurt, oil, minced garlic, flour, baking powder, and salt. Mix until the dough comes together. 
		\step Turn dough out onto lightly floured surface. Use floured hands to knead the dough until smooth, about 3 to 5 minutes. 
		\step Place dough into greased container and cover with plastic wrap. Let rest at room temperature for about an hour, until doubled in size. 
		\step When ready to cook, divide the dough into 10 equal pieces. Roll into balls, then use a rolling pin to roll each ball into a large oval about 6-inches long and $\sfrac{1}{8}$-inch thick. 
		\step Heat a large cast iron skillet over medium high heat. Grease with a small amount of oil. 
		\step Place one piece of the naan on the oiled hot skillet and cook until bubbles form on top, about 1 to 2 minutes. While cooking, brush the top with a little oil. 
		\step Flip and cook for another 1 to 2 minutes, until large golden spots appear on the bottom. 
		\step Remove from the skillet and wrap in a clean kitchen towel. Repeat with the remaining naan. 
		\step \textbf{For the topping:} Combine melted butter and minced garlic together in a bowl. Brush each naan with the garlic butter and top with the fresh herb of your choosing. Do not top if you plan on storing. 
    }
	
	\hint
	{
		They can be stored on the counter (2 days), in the fridge (4 days), or in the freezer (2 months).
	}

\end{recipe}
