\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Rayn,
]
{Mashed Potatoes and Parsnips}
    
    \ingredients
    {
		2$\sfrac{1}{2}$ & lb red potatoes \\
		1 & lb parnsips \\
		1 & cup heavy cream \\
		$\sfrac{1}{2}$ & head of garlic, roasted \\
		4 & Tbsp butter \\
		2 & cups parmesan \\
		dash & salt and pepper \\
    }
    
    \preparation
    {
        \step Peel the parsnips and chop them into medium chunks. 
		\step Remove eyes from potatoes and peel if not using red potatoes. Chop into size of parsnip chunks. 
		\step Put parsnips and potatoes into a large pot and cover with water. Add a hefty pinch of salt (less than for pasta water) -- roughly a heaping teaspoon. 
		\step Boil until soft. 
		\\
		\step When the carbs are soft to the fork touch, drain them. Add butter. \\
		\step ``Begin the smashing process, and get all the latent rage out.''
		\\
		\step Add half the heavy cream and continue smashing. Add the roasted garlic and continue smashing. 
		\step Salt liberally, to taste, and a healthy amount of black pepper. Add the parmesan. \\(``I just add the whole bag every time cause cheese.'')
		\step Taste, and add cream until desired consistency is achieved (i.e., the rest of it). 
    }

	\suggestion[Roasted Garlic]
	{
		Peel the garlic. Place peeled cloves in medium size of aluminum foil and make it into a little packet, adding about 3~Tbsp of olive oil. Bake packet at 400$^{\circ}$F for 25~to 30~minutes, until the cloves are golden brown and melty. \\
		\\
		They will keep for up to a week. 
	}
	
	\hint
	{
		Half a head of garlic roasted $=$ 1~teaspoon of garlic powder. 
	}

\end{recipe}
