\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Field's via Mom,
]
{Peanut Butter Cookies}

    \ingredients
    {
		2 & cups AP flour \\
		 & (240 g) \\
		\sfrac{1}{2} & tsp baking soda \\
		\sfrac{1}{4} & tsp salt \\
		 & \\
		1\sfrac{1}{4} & cups dark brown sugar, firmly packed \\
		 & (266 g) \\
		1\sfrac{1}{4} & cups white sugar \\
		 & (248 g) \\
		 & \\
		1 & cup salted butter, softened \\
		 & \\
		3 & large eggs \\
		1 & cup creamy peanut butter \\
		2 & tsp vanilla extract \\
    }
    
    \preparation
    {
        \step Preheat oven to 300$^{\circ}$~F. \\
		\step In a medium bowl combine flour, baking soda, and salt. Mix well with a wire whisk and set aside. 
		\step In a large bowl blend sugars using an electric mixer set at medium speed. Add butter and mix to form a grainy paste, scraping the sides of the bowl.
		\step Add eggs, peanut butter, and vanilla; mix at medium speed until light and fluffy. 
		\step Add the flour mixture and mix at low speed until just mixed. Do not overmix. 
		\step Drop by rounded tablespoons (\#30 scoop?) onto an ungreased cookie sheet, 1\sfrac{1}{2} inches apart. With a wet fork, gently press a crisscross pattern on top of cookies. 
		\step Bake for 18-22 minutes until cookies are slightly brown along edges. Transfer cookies immediately to cool surface with a spatula. 
    }
	
	\suggestion
	{
		As a variation, add 2~cups coarsely chopped semisweet chocolate bar or 2~cups semisweet chocolate chips to the flour mixture, then bake as directed. 
	}
	
	\hint
	{
		Makes 3\sfrac{1}{2} dozen cookies
	}

\end{recipe}
