\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Inspired by Mahogany Grill in Ithaca,
% https://barefootcontessa.com/recipes/penne-alla-vodka
]
{Penne Alla Vodka}

    \ingredients
    {
		$\sfrac{1}{4}$ & cup good olive oil \\
		2 & yellow onions, chopped \\
		 & \\
		3 & garlic cloves, minced \\
		$1\sfrac{1}{2}$ & tsp oregano \\
		$\sfrac{1}{2}$ & tsp red pepper flakes \\
		 & \\
		1 & cup vodka \\
		56 & oz canned whole peeled plum tomatoes, drained \\
		 & \\
		1 & cup heavy cream \\
		1 & lb cooked penne \\
		$\sfrac{1}{2}$ & c grated parmesan \\
    }
    
    \preparation
    {
        \step Preheat the oven to 375$^{\circ}$F. \\
		\step Heat the oil in a Dutch oven over medium-low heat. Add the onions and cook for about 5~minutes, until the onions are translucent. 
		\step Add the garlic, oregano, and red pepper flakes and cook for just one minute.
		\step Add the vodka and simmer for 5 to 7~minutes, until the mixture is reduced by half. 
		\step With clean hands, crush each tomato into the pot. Add 2~tsp salt and $\sfrac{1}{2}$~tsp black pepper.
		\step Cover the pot with a tight-fitting lid and bake for $1\sfrac{1}{2}$ hours. 
		\step Meanwhile, bring a large pot of salted water to boil and cook penne. Drain and set aside. (Start after $\sim$1~hour)
		\step Pour the tomato mixture into a food processor or blender and puree until smooth. 
		\step Return the tomato mixture to the pot. Add the cream, 1~tsp salt, $\sfrac{1}{2}$~tsp black pepper, and more oregano to taste and simmer partially covered for 10~minutes.
		\step Add the cooked pasta to the sauce and cook for 2~more minutes. \\
		\step Remove from heat and stir in parmesan; serve with extra parmesan and fresh oregano. 
    }

\end{recipe}
