\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5-6},
    source = Florence Shultz's recipe for cinnamon rolls
%	the recipe card was found in Evelyn Deitrick's recipe box, in Evelyn's handwriting.
]
{Refrigerator Rolls}

    \ingredients
    {
		1 & packet of active yeast \\
		$\sfrac{1}{2}$ & cup lukewarm water \\
		 & \\
		$\sfrac{2}{3}$ & cup shortening \\
		99 & g sugar \\
		 & ($\sfrac{1}{2}$~cup) \\
		2 & tsp salt \\
		1 & cup mashed potatoes \\
		1 & cup scalded milk \\
		 & \\
		2 & eggs, well-beaten \\
		600 & g AP flour \\
		 & (5~cups) \\
		 & \\
		\multicolumn{2}{l}{\textbf{Filling}} \\
		4 & Tbsp AP flour \\
		200 & g brown sugar \\
		3 & Tbsp cinnamon \\
		 & \\
		2 & Tbsp melted butter \\
    }
    
    \preparation
    {
        \step Dissolve yeast in water and set aside. \\ 
		\step Heat mashed potatoes and stir in shortening until combined or melted. 
		\step Add mashed potatoes, shortening, sugar, and salt to scalded milk in mixing bowl. When cool ($< 110^{\circ}$F), add dissolved yeast. 
		\step Mix thoroughly and add eggs. Slowly add flour to mixture.
		\step Turn onto slightly floured board and knead well -- about 5~minutes. Place in bowl, cover tightly, and place in refrigerator. 
		\step About 1~hour before baking, remove dough from fridge, split in half, and shape each half into rough rectangle approximately 12"x~20". Combine flour, brown sugar, and cinnamon in separate bowl. 
		\step Cover each rectangle with roughly half of the filling, leaving a thin strip along a longer edge uncovered; seperate into 16 strips. 
		\step Roll up strips (tucking tail beneath roll) and place onto sheets; brush with melted butter. Cover and let rise until light (roughly an hour).  
%		\step About 1~hour before baking, pinch off dough, shape into rolls as desired. Cover and let rise until light. 
		\step Bake in 425$^{\circ}$F oven for 12 to 20~minutes; internal temp should be 190$^{\circ}$F. Makes 32 rolls. 
    }
	
	\hint
	{
		Make same as cinnamon rolls. Place cut roll in pan which has melted oleo (margarine) and brown sugar. Bake in hot oven and remove from pan immediately. 
	}

\end{recipe}
