\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = David's ATK Subscription and Elise's old slow-cooker,
%	https://www.americastestkitchen.com/recipes/10660-slow-cooker-parmesan-risotto
]
{Slow Cooker Parmesan Risotto}

    \ingredients
    {
		1 & white onion, finely chopped \\
		4 & Tbsp unsalted butter \\
		3 & garlic cloves, minced \\
		$\sfrac{1}{4}$ & tsp dried thyme (1 tsp fresh) \\
		$\sfrac{1}{2}$ & tsp salt \\
		 & \\
		5 & cups vegetable or chicken broth, plus extra \\
		$\sfrac{1}{2}$ & cup dry white wine \\
		 & \\
		2 & cups Arborio rice \\
		 & \\
		2 & oz Parmesan cheese, grated (1 cup) \\
		2 & Tbsp fresh chives, minced \\
		1 & tsp lemon juice \\
    }
    
    \preparation
    {
        \step Lightly coat the oval slow cooker with vegetable oil spray. Microwave onion, 2~Tbsp butter, garlic, thyme, and salt in bowl, stirring occasionally, until onion is softened, about 5~minutes; transfer to slow cooker. 
		\step Microwave 2~cups broth and wine 4-cup container until steaming, about 5~minutes. Stir broth mixture and rice into slow cooker.
		\step Gently press sheet of parchment paper onto surface of broth mixture, folding down the edges as needed. Cover and cook until rice is almost fully tender and all liquid is absorbed, 2~to 3~hours on high. 
		\step Microwave remaining 3~cups of broth in previous container until steaming, about 5~minutes. Discard parchment. Slowly stream broth into rice, stirring gently, until liquid is absorbed and risotto is creamy, about 1 minute.
		\step Gently stir in remaining 2~Tbsp of butter, Parmesan, chives, and lemon juice until combined. Adjust consistency with extra hot broth as needed. Season with salt and pepper to taste and serve. 
    }

\end{recipe}
