\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = S'mores craving and the internet,
%	https://www.melskitchencafe.com/smores-hershey-kiss-blossom-cookies/
]
{S'mores Hershey Kiss Cookies}

    \ingredients
    {
		177 & g AP flour \\
		\sfrac{1}{2} & tsp baking powder \\
		\sfrac{1}{4} & tsp baking soda \\
		\sfrac{1}{4} & tsp salt \\
		 & \\
		8 & Tbsp unsalted butter, softened \\
		50 & g sugar \\
		50 & g light brown sugar \\
		85 & g graham cracker crumbs, plus 28~g for topping \\
		 & \\
		1 & large egg \\
		1 & tsp vanilla extract \\
		 & \\
		12 & marshmallows cut in half \\
		24 & Hershey's Kisses, unwrapped 
    }
    
    \preparation
    {
        \step Preheat the oven to 350$^{\circ}$F. Line two large, rimmed baking sheets with parchment paper, silpat liner, or lightly grease with cooking spray.
		\step In a bowl, whisk together the flour, baking powder, baking soda, and salt. 
		\step Using an electric handheld mixer or in the bowl of a stand mixer fitted with the paddle attachment, beat together the butter, sugars, and graham cracker crumbs for 2-3 minutes, until light and creamy. 
		\step Add the egg and vanilla and mix. Add the flour mixture and mix until just combined. 
		\step Measure out about a tablespoon (\#60 scoop) and roll into a ball. Roll the cookie dough ball in the ``topping'' graham cracker crumbs to coat lightly. 
		\step Place the cookie dough on the prepared baking sheets, 12 per sheet. Bake one sheet at a time for 8-10 minutes until the cookies are just starting to crack a bit; they should still be soft. Let them cool for a minute or two on the baking sheet. 
		\step Preheat the broiler, making sure an oven rack is about 10-inches below the heating element. Place a marshmallow half, cut side down, on top of each cookie and broil the marshmallows for about 30 seconds, watching closely! They should be golden brown and soft.
		\step Working quickly, immediately push a Hershey's Kiss gently into the center of each soft marshmallow. 
		\step Repeat with the remaining cookie sheet - you may find it helpful to turn the oven off for a few minutes before setting it back to 350$^{\circ}$~F. 
		\step Let the cookies cool until the Hershey's Kiss has set up again. 
    }
	
	\suggestion
	{
		Cut the marshmallows in half crosswise -- like a hamburger bun. You'll get two marshmallows with the original diameter and half as high. 
	}
	
	\suggestion[Convection Oven]
	{
		If using a convection oven, bake at 325$^{\circ}$F. 
	}
	
	\hint
	{
		If referring back to the original recipe, use the weights, not the volumes -- the two don't seem to match up. 
	}

\end{recipe}
