\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = King Arthur Baking,
%	https://www.kingarthurbaking.com/recipes/sourdough-banana-bread-recipe
]
{Sourdough Banana Bread}

    \ingredients
    {
		8 & Tbsp unsalted butter, room temp \\
		142 & g brown sugar \\
		 & ($\sfrac{2}{3}$~cup, packed)\\
		1 & tsp vanilla extract \\
		1 & tsp baking soda \\
		1 & tsp baking powder \\
		1 & tsp salt \\
		 & \\
		397 & g mashed ripe bananas (4-5)\\
		85 & g honey ($\sfrac{1}{4}$~cup) \\
		2 & eggs \\
		113 & g sourdough starter \\
		 & \\
		240 g & AP flour \\
		85 & g chopped nuts, optional \\
    }
    
    \preparation
    {
        \step Preheat the oven to 325$^{\circ}$F. Lightly grease a 9"x 5" loaf pan.
		\step In a large bowl, combine the butter, sugar, vanilla, baking soda, baking powder, and salt -- beating until smooth.
		\step Add the mashed bananas, honey, eggs, and sourdough starter -- again beating until smooth. 
		\step Add the flour then nuts, stirring just until smooth. 
		\step Transfer the batter to the prepared loaf pan, smoothing the top. Let it rest at room temperature for 10 minutes. 
		\step Bake the bread for 40 minutes, then gently lay a piece of aluminum foil across the top. 
		\step Bake for an additional 30 minutes. Remove the bread from the oven; a long toothpick or thin paring knife inserted into the center should come out clean, with a few wet crumbs clinging to it. If the tester shows any sign of uncooked batter, cook for an additional 5 minutes, or until it tests done. 
		\step Allow the bread to cool for 10 minutes in the pan. Remove it from the pan and cool completely on a rack. 
		\step Store leftover bread, tightly wrapped, at room temperature for several days. Freeze for longer storage. 
    }

\end{recipe}
