\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = King Arthur Baking,
%	https://www.kingarthurbaking.com/recipes/sourdough-pumpkin-spice-bread-recipe
]
{Sourdough Pumpkin Spice Bread}

    \ingredients
    {
		67 & g vegetable oil \\
		 & ($\sfrac{1}{3}$~cup) \\
		99 & g light brown sugar \\
		84 & g honey \\
		  & ($\sfrac{1}{4}$~cup) \\
		2 & eggs \\
		425 & g pumpking pure\'e \\
		 & \\
		170 & g sourdough starter, unfed/discard \\
		1 & tsp vanilla extract \\
		 & \\
		240 & g AP flour \\
		$\sfrac{3}{4}$ & tsp salt \\
		$\sfrac{3}{4}$ & tsp cinnamon \\
		$\sfrac{3}{4}$ & tsp ginger \\
		$\sfrac{3}{4}$ & tsp cloves \\
		$\sfrac{3}{8}$ & tsp nutmeg \\
		$\sfrac{1}{2}$ & tsp baking powder \\
		$\sfrac{3}{4}$ & tsp baking soda \\
		 & \\
		57 & g chopped walnuts \\
		85 & g raisins \\
    }
    
    \preparation
    {
        \step Preheat the oven to 350$^{\circ}$F. Lightly grease a 9"x 5" loaf pan.
		\step In a large bowl, stir together the oil, sugar, honey, eggs, and pumpkin. Stir in the starter and vanilla.
		\step In a medium bowl, whisk together the flour, salt, spices, baking powder, and baking soda. Stir the dry ingredients into the wet until evenly combined. Stir in the nuts and raisins. 
		\step Transfer the batter to the prepared pan and bake for 60 to 65~minutes, until a paring knife inserted in the center comes out clean. 
		\step Remove the bread from the oven and cool it in the pan on a rack for 15~minutes before turning it out of the pan back onto the rack. Allow the bread to finish cooling completely before slicing. 
		\step Store the bread, tightly wrapped in plastic, at room temperature for several days; freeze for longer storage. 
    }

\end{recipe}
