\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Mom,
]
{Mrs.~Arnold's Spritz Cookies}

    \ingredients
    {
		2 & cups butter, room temperature \\
		2 & cups granulated sugar \\
		 & (396 g) \\
		1 & Tbsp vanilla extract \\
		4 & eggs \\
		 & \\
		2 & cups finely chopped or ground walnuts \\
		6 & cups AP flour \\
		 & (720 g) \\
		1 & tsp baking powder \\
		& food dyes (optional) \\
    }
    
    \preparation
    {
        \step In extra-large bowl, use electric mixer to beat together butter, granulated sugar, vanilla, and eggs until fluffy.
		\step Gradually beat in walnuts, flour, and baking powder, blending thoroughly. 
		\step Divide dough into 2 portions. Use dough immediately or wrap and refrigerate up to 3 days. If dough has been chilled, let stand at room temperature until pliable enough to press through a cookie press.
		\step To bake cookies, preheat oven to 375$^{\circ}$~F. Fill a cookie press with dough. Stand cookie press upright on cold ungreased baking sheet. Force dough out to form shape; release pressure and lift up slightly to cut off dough. Cookies should be 1$\sfrac{1}{2}$ inches apart. Bake 8 to 10 minutes or until bottoms are golden; tops should be pale, not brown. 
    }
    
    \hint
    {
        Chocolate Spritz: Add $\sfrac{1}{4}$~cup unsweetened cocoa to $\sfrac{1}{4}$ recipe of the dough, blending thoroughly. Bake at 375$^{\circ}$~F for 5 to 7 minutes or until bottoms are lightly browned.
    }

\end{recipe}
