\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
    portion = \portion{6-8},
    source = Aunt Donna -- Betty Crocker,
%	https://www.bettycrocker.com/recipes/taco-fiesta-chicken-lasagna/124ea066-bab5-4df8-bbf5-becde1b2623f
]
{Taco Fiesta Chicken Lasagna}
    
    \ingredients
    {
		29 & oz can of diced tomatoes with zesty mild green chiles, undrained \\
		$\sfrac{1}{4}$ & cup taco sauce \\
		3 & cups cubed cooked chicken \\
		 & \\
		16 & oz can of Old El Paso Refried Beans \\
		$\sfrac{1}{2}$ & cup sour cream \\
		 & \\
		12 & uncooked lasagna noodles \\
		3 & cups shredded Colby-Monterey Jack cheese \\
		$\sfrac{1}{2}$ & cup green onions, chopped \\
		 & \\
		 & cherry salsa for topping \\
    }
    
    \preparation
    {
        \step Spray 15x12-inch sheet of foil and 13x9-inch glass baking dish with nonstick cooking spray. 
		\step In large bowl, combine tomatoes and taco sauce; mix well. Stir in chicken. 
		\step In medium bowl, combine refried beans and sour cream; mix well. 
		\step Spread about 1~cup of chicken mixture in bottom of dish. Top with 4 uncooked noodles, breaking to fit if necessary. Spread with half of bean mixture and 1$\sfrac{1}{2}$~cups of chicken mixture. Sprinkle with 1~cup of cheese and half of the onions. 
		\step Layer 4 more noodles, remaining bean mixture, 1$\sfrac{1}{2}$~cups chicken mixture, and 1~cup of cheese. 
		\step Top with remaining 4 noodles, chicken mixture, onions, and cheese. Be sure top noodles are covered. 
		\step Cover with foil, sprayed side down. Refrigerate at least 8 hours or overnight. 
		\step Heat oven to 350$^{\circ}$F. Bake covered lasagna for 50~minutes. Uncover dish and bake an additional 18~to 22~minutes or until bubbly and thoroughly heated. Let stand 10~minutes before serving.
    }
	
	\hint
	{
		Buy $\sfrac{1}{2}$-inch thick slices of cooked chicken from deli and cube the slices (1.25~lb)
	}

\end{recipe}
