\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Weird Texas nostalgia for breakfast containing meat and no eggs,
%	https://www.allrecipes.com/recipe/268998/texas-sausage-kolaches-klobasneks/ (primary)
%	https://houseofyumm.com/sausage-kolaches/ (some inspiration)
]
{Texas Kolaches}

    \ingredients
    {
		\multicolumn{2}{l}{\textbf{Kolaches}} \\
		$\sfrac{1}{2}$ & c milk \\
		99 & g white sugar ($\sfrac{1}{2}$~c)\\
		1 & tsp salt \\
		4 & Tbsp unsalted butter, melted \\
		 & \\
		2 & ($\sfrac{1}{4}$~oz) packages active dry yeast \\
		$\sfrac{1}{2}$ & c warm water \\
		 & \\
		2 & large eggs \\
		540 & g AP flour ($4\sfrac{1}{2}$~c) \\
		 & \\
		12 -- 18 & sausages, hot dog size, cooked \\
		8 -- 11 & cheddar slices \\
		\multicolumn{2}{l}{\textbf{Egg wash}} \\
		1 & egg \\
		1 & tsp milk \\
	}
    
    \preparation
    {
        \step Heat milk in a small saucepan over medium heat until it begins to bubble; remove from heat immediately. Stir in sugar, salt, and melted butter until sugar is dissolved. Set aside to cool to room temperature, about 10 minutes. 
		\step Beat eggs in a small bowl. Combine warm water ($100-110^{\circ}$F) and yeast in a large bowl of a stand mixer and stir until dissolved. Add a pinch of sugar, and let sit until foamy. 
		\step Stir in cooled milk mixture, eggs, and 240~g (2~c) flour. Beat using the dough hook until smooth. Add remaining flour (300~g), mixing as you go, just until dough is elastic and slightly stiff, but not dry. 
		\step Turn dough out onto a floured board and knead until smooth and very elastic, 10 to 15 minutes. Coat dough lightly with butter or oil and place in a bowl. Cover with plastic wrap or a damp towel and let sit in a warm place to double in size, about 1 hour. 
		\step Pat the sausages dry and preheat the oven to $350^{\circ}$F. Prepare the baking sheets with parchment paper. 
		\step Turn risen dough onto a very lightly floured board. Roll into a log, cut into 6 equal slices, and cut each slice into either 2 or 3 pieces (depends on number of sausages). 
		\step Use the palm of your hand to flatten and press each piece into a rectangle, about the length and slightly more than the circumference of the sausage. Place the cheddar slice, then the sausage; roll dough around fillings and very tightly pinch the seam together to seal. Repeat with remaining dough, sausage, and cheddar. 
		\step Mix together egg wash ingredients in a small bowl and brush egg wash over the dough. Bake in preheated oven until golden, 12 to 15 minutes. 
    }
	
	\suggestion[]
	{
		18 sausages had slightly more than the bare amount of dough -- go for 12 sausages to get the full fluffy dough effect. 
	}

\end{recipe}
