\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Taste of Thai Express during first time running an accelerator,
	%https://carlsbadcravings.com/thai-red-curry-chicken-recipe/
]
{Thai Red Curry}

    \ingredients
    {
		1$\sfrac{1}{2}$ & Tbsp olive oil \\
		1 & lb chicken, chopped \\
		2 & Tbsp red curry paste \\
		1 & large onion, 2" thin strips \\
		1 & red bell pepper, 2" thin strips \\
		1 & orange bell pepper, 2" thin strips \\
		 & \\
		2 & tsp ginger, grated \\
		4 & garlic cloves, minced \\
		 & \\
		13.5 & oz can of coconut milk \\
		1 & Tbsp cornstarch \\
		1 & Tbsp Thai Sweet Chili Sauce (Mae Ploy) \\
		2 & Tbsp soy sauce \\
		2 & Tbsp fish sauce \\
		2 & Tbsp lime juice \\
		1 & Tbsp brown sugar \\
		1 & bay leaf \\
		1 & tsp basil \\
		$\sfrac{1}{4}$ & tsp salt \\
		$\sfrac{1}{4}$ & tsp pepper \\
    }
    
    \preparation
    {
        \step Heat oil over medium high heat in large nonstick skillet. Add chicken, onion, bell pepper, and red curry paste and cook just until chicken is no longer pink. 
		\step Add ginger and garlic and saute 1 minute.
		\\
		\step Add half of the coconut milk. Mix remaining coconut milk with cornstarch and add to skillet with all remaining ingredients.
		\step Bring to a boil, then reduce to a simmer for 5 minutes or until the sauce thickens and the vegetables reach desired tenderness. 
		\step Discard bay leaf and serve with rice. 
    }
	
	\hint
	{
		Start coconut rice first, and let that cook while preparing curry. 
	}

\end{recipe}
