\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Plague-time quarantine desire,
	%https://www.askchefdennis.com/the-best-tiramisu-you-will-ever-make/
]
{Tiramisu}

    \ingredients
    {
		9 & large egg yolks \\
		1$\sfrac{1}{2}$ & cup sugar \\
		 & (300~g) \\
		440 & g mascarpone cheese \\
		624 & g heavy whipping cream \\
		3 & packages of soft ladyfingers \\
		1$\sfrac{1}{2}$ & cups cold espresso or strong coffee (see Mocha Frappuccino recipe) \\
		$\sfrac{3}{4}$ & cup Kahlua \\
		dash & unsweetened cocoa \\
	}
    
    \preparation
    {
        \step In very large bowl, whisk together egg yolks and sugar in the top of a double boiler, over boiling water. 
		\step Reduce the heat to low (water should be simmering), and cook for about 10 minutes, stirring constantly with a wire whisk. This is your sabayon, remove from heat and continue to whip yolks until thick and lemon-colored. Allow to cool briefly before mixing in mascarpone.
		\step Add room temperature mascarpone to whipped yolks, mix until well combined. 
		\step In a separate bowl, use an electric mixer to whip cream to stiff peaks. Mixer speed should start low before gradually increasing, taking about 10 minutes. 
		\step Gently fold whipped cream in the mascarpone sabayon mixture and set aside. 
		\step Mix cold espresso with coffee liquor and dip ladyfingers into the mixture just long enough to get them wet -- do not soak them! 
		\step Arrange ladyfingers in bottom of dish(es). 
		\\
		\step Spoon half the mascarpone cream filling over the ladyfingers.
		\\
		\step Repeat process with another layer of ladyfingers and add another layer of mascarpone cream. 
		\step Refrigerate at least 6~hours; overnight is better. 
		\\
		\step Dust with cocoa before serving. 
    }
	
	\suggestion[Things to Keep in Mind]
	{
		Eggs and mascarpone should be room temperature for best results. \\
		\\
		Do not under whip the sabayon. \\
		\\
		Always use the freshest products available. If the eggs, cream, or mascarpone are close to the expiration date, they can break down in the recipe. 		
	}
	
	\suggestion
	{
		To freeze, place plastic wrap directly against surface (without cocoa) to prevent a skin from forming and cover tightly. Repeat the process with an additional layer of plastic wrap and then cover with tin foil and freeze. To defrost, let it sit at room temperature for 15 to 20 minutes. Add cocoa and serve. 
	}
	
	\hint
	{
		Makes either (1) 9"x 13" pan or (2) 8"x 8" pans. 		
	}

\end{recipe}
