\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Treebeards' via Mom,
]
{Treebeards' Shrimp Etouffee}
    
    \ingredients
    {
		1 & cup butter \\
		2$\sfrac{2}{3}$ & cups celery, $\sfrac{1}{2}$-inch pieces \\
		2 & medium onions, $\sfrac{1}{2}$-inch pieces \\
		1 & bell pepper, $\sfrac{1}{2}$-inch pieces \\
		 & \\
		1$\sfrac{1}{4}$ & tsp salt \\
		>$\sfrac{1}{8}$ & tsp cayenne pepper \\% (rounded) \\
		<$\sfrac{3}{4}$ & tsp black pepper \\%(scant) \\
		<$\sfrac{3}{4}$ & tsp garlic powder \\%(scant) \\
		<$\sfrac{3}{4}$ & tsp ground thyme \\%(scant) \\
		 & \\
		2 & cups boiling water, mixed with \\
		1 & tsp shrimp base \\
		$\sfrac{1}{8}$ & tsp liquid crab boil \\
		$\sfrac{1}{2}$ & tsp hot sauce \\
		4 & tsp Worcestershire sauce \\
		$\sfrac{1}{3}$ & cup AP flour \\
		2 & cups green onions (including tops), chopped \\
		$\sfrac{1}{3}$ & cup fresh parsley, chopped \\
		4 & tsp tomato paste \\
		2 & lb Treebeards' shrimp \\
    }
    
    \preparation
    {
        \step In heavy 5-quart Dutch oven or saucepan over medium heat, melt butter. 
		\step Add celery, onions, and bell pepper. Stirring occasionally, cook until vegetables are soft, about 20~to 25~minutes. 
		\step In small bowl, mix spices, shrimp base broth, crab boil, hot sauce, and Worcestershire sauce. 
		\step When vegetables are soft, add flour and cook, stirring, for 2~minutes. 
		\step Add spice mixture, continue to cook for 5~minutes more. 
		\step Stir in green onions, parsley, and tomato paste and simmer until vegetables are tender. 
		\step Add shrimp and cook only until shrimp are heated through. 
		\step Serve over hot rice. 
		\\
		\\
		\\
		\\
		\\
		\\
		\\
		\\ 
    }

	\suggestion
	{
		May substitute shrimp base for fish base or lobster base. 
	}

\end{recipe}
