\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = Craving during the plague times,
	%https://www.delish.com/cooking/recipe-ideas/recipes/a54955/easy-wonton-soup-recipe/
]
{Wonton Soup}

    \ingredients
    {
		\multicolumn{2}{l}{\textbf{For the wontons}} \\
		1 & lb ground pork \\
		1 & Tbsp soy sauce \\
		1 & Tbsp chives, thinly sliced \\
		1$\sfrac{1}{2}$ & tsp rice wine vinegar \\
		1$\sfrac{1}{2}$ & tsp cornstarch \\
		1$\sfrac{1}{2}$ & tsp ginger, grated \\
		2 & garlic cloves, minced \\
		$\sfrac{1}{2}$ & tsp red pepper flakes \\
		$\sfrac{3}{4}$ & tsp sesame oil \\
		1 & package square wonton wrappers \\
		\multicolumn{2}{l}{\textbf{For the soup}} \\
		8 & cups chicken broth \\
		2 & inch ginger root, peeled \\
		2 & tsp soy sauce \\
		2 & garlic cloves, smashed \\
		$\sfrac{1}{4}$ & tsp sesame oil \\
		2 & Tbsp sliced green onions, for garnish \\
    }
    
    \preparation
    {
        \step In a bowl, mix all wonton ingredients except wrappers until fully incorporated.
		\step Fill a small bowl with water. Using your finger, wet the edges of wonton wrapper with water. Place half a tablespoon of filling in the center of wonton wrapper. Fold wonton in half diagonally to create a triangle, and seal the edges. Fold the two identical corners in on each other and press again to seal. Repeat until all filling is used.
		\step Bring all soup ingredients to a boil. Reduce heat to low and simmer for 10~minutes, then remove ginger and garlic cloves. 
		\step Bring it back to a boil. Lower in wontons and cook for 5~minutes, or until floating. Serve into bowl and garnish with green onions. 
    }
	
	\hint
	{
		Wontons can be prepped, then frozen. Soup ingredients need to be doubled for amount of wontons.
	}

\end{recipe}
