\setHeadlines
{
}

\begin{recipe}
[ % Optionale Eingaben
%    preparationtime = {1]{h}},
%    portion = \portion{5},
    source = ATK via Elise, 
]
{Zucchini Bread}

    \ingredients
    {
		5$\sfrac{1}{2}$ & oz whole-wheat flour \\
		5 & oz AP flour \\
		1 & tsp salt \\
		1 & tsp ground cinnamon \\
		1 & tsp baking powder \\
		1 & tsp baking soda \\
		$\sfrac{1}{2}$ & tsp ground nutmeg \\
		 & \\
		7 & oz brown sugar \\
		2 & eggs \\
		$\sfrac{1}{4}$ & cup vegetable oil \\
		1 & tsp vanilla extract \\
		 & \\
		1$\sfrac{1}{2}$ & lb zucchini \\
    }
    
    \preparation
    {
        \step Put oven rack in middle position and pre-heat oven to 325$^{\circ}$F. Lightly grease 9"x 5" loaf pan. 
		\step In medium bowl, whisk together whole-wheat flour, AP flour, salt, cinnamon, baking powder, baking soda, and nutmeg; set aside. 
		\step In large bowl, whisk together brown sugar, eggs, oil, and vanilla. 
		\step Trim off ends of zucchini. Shred zucchini on large holes of box grater and squeeze dry in dish towel. 
		\step Stir zucchini into bowl with brown sugar mixture; use rubber spatula to stir until combined. 
		\step Add flour mixture and use spatula to gently stir until just combined and no dry flour is visible. Do not overmix. 
		\step Scrape batter into prepared loaf pan and smooth top. Bake until zucchini bread is golden brown and toothpick inserted in center comes out clean, 65 to 75 minutes. The interior shoud be 200$^{\circ}$F.
		\step Place loaf pan on cooling rack and let bread cool in pan for 15~minutes. \\
		\step Remove zucchini bread from pan and let cool on rack for at least 1~hour. 
    }


\end{recipe}
